---
title: "Evaluate XGBoost Models"
author: "William E Fondrie"
---
```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, results = "hide")
```

## Load Libraries & Prepare Workspace
```{r loadLibraries, results = "hide"}
# data manipulation
suppressMessages(library(tidyverse, quietly = T))
library(stringr, quietly = T)
library(forcats, quietly = T)
library(broom, quietly = T)

# machine learning tools
library(PRROC, quietly = T)
library(caret, quietly = T)
library(xgboost, quietly = T)

# for session info
library(devtools, quietly = T)

# ggplot2 theme
source("../R/ggplotTheme.R")
theme_set(coolTheme)

# other functions
source("../R/prepareData.R")
source("../R/utilityFunctions.R")

# for reproducibility
set.seed(0847532)

# Bootstrap
nboot <- 2000 #2000

# for barplots
dodge <- position_dodge(width = 0.9)
```

## Evaluation of Model Performance on Isolate Spectra in Library
```{r singles}
testList <- readRDS("../temp/testDatList.rds")
testdmatList <- prepareData(testList, orgLabs = c("Ab", "Kp"))

mods <- readRDS("../temp/finalModels.rds")

formatResults <- function(model, dataList) {
    results <- as.data.frame(predict(model, dataList$dat, reshape = T))
    names(results) <- levels(unique(dataList$encoding)[[1]])
    
    results <- results %>%
        mutate(truth = dataList$encoding[[1]],
               negVsAll = pos + other,
               posVsAll = neg + other,
               speciesVsOther = pos + neg,
               pred = ifelse(neg > pos & neg > other, "neg", NA),
               pred = ifelse(pos > neg & pos > other, "pos", pred),
               pred = ifelse(other > neg & other > pos, "other", pred))
    
    return(results)
}

```

### Import Acinetobacter baumannii
```{r AbSingleSpec, results='markup'}
abMod <- xgb.load(mods$Ab)
abRes <- formatResults(abMod, testdmatList$Ab)

# Ab PR curves
abPr <- makePrCurves(abRes)

# Ab ROC curves
abRoc <- makeRocCurves(abRes)

saveRDS(abRes, file = "../temp/abRes.rds")

# Ab curve statistics
abCurveStat <- abRes %>%
    bootstrap(nboot) %>%
    do(calcAUC(.)) %>%
    mutate(org = "Ab")
```

### Import Klebsiella pneumoniae
```{r KpSingleSpec, results="markup"}
kpMod <- xgb.load(mods$Kp)
kpRes <- formatResults(kpMod, testdmatList$Kp)

# Kp PR curves
kpPr <- makePrCurves(kpRes)

# Kp ROC curves
kpRoc <- makeRocCurves(kpRes)

saveRDS(kpRes, file = "../temp/kpRes.rds")

# Kp curve statistics
kpCurveStat <- kpRes %>%
    bootstrap(nboot) %>%
    do(calcAUC(.)) %>%
    mutate(org = "Kp")


# Aggregate stats 
curveStat <- abCurveStat %>%
    full_join(kpCurveStat) %>% 
    group_by(org, type, level) %>%
    summarize(avg_AUC = mean(AUC),
              ci_low = quantile(AUC, 0.05 / 2),
              ci_high = quantile(AUC, 1 - 0.05 / 2)) %>%
    mutate(classifier = "XGBoost")
    
```

### Plot PR and ROC Curves
#### Plot function
```{r plotFunction}
# dat should be the ouput of PRROC::pr.curve(..., curve = T) or roc.curve(..., curve = T)
plotCurve <- function(dat, type = "ROC", title = NULL) {
    dat <- dat %>%
        mutate(classifier = fct_rev(as.factor(classifier)),
               Level = fct_rev(as.factor(Level)))
    
    # Main Plotting
    p <- ggplot(dat, aes(x = V1, y = V2, linetype = classifier, color = Level))
    
    if(type == "ROC") {
        p <-  p + geom_abline(intercept = 0, slope = 1) +
            xlab("1 - Specificity (FPR)") +
            ylab("Sensitivity (TPR)")
    } else {
        p <- p + xlab("Recall") +
            ylab("Precision")
    }
    
    # Common theming
    p <- p + geom_path(size = 0.5) +
        ylim(c(0, 1)) +
        xlim(c(0, 1)) +
        scale_color_discrete(name = "Level") +
        scale_linetype_discrete(name = "Classifier") +
        coord_equal()+
        labs(title = title) +
        theme(legend.key.height = unit(0.6, "lines"),
              legend.key.width = unit(0.6, "lines"),
              legend.margin = margin(l = -0.5, 
                                     r = -0.5,
                                     unit = "lines"))
    
    return(p)
}
```

#### Import baseline classifier results  
```{r importBaselineResults}
sfRes <- readRDS("../temp/sfRes.rds")
sfCurveStat <- readRDS("../temp/sfCurveStat.rds") %>%
    mutate(classifier = "Single Feature")
```

#### Function to Format ROC and PR results
```{r formatCurveResults}
combineResults <- function(mlResults, 
                           sfResults, 
                           type = "species") {
    ml <- as.tibble(mlResults[[type]]$curve) %>% mutate(classifier = "XGBoost")
    sf <- as.tibble(sfResults[[type]]$curve) %>% mutate(classifier = "Single Feature")
    
    r <-  ml %>% rbind(sf) %>% 
        mutate(type = type,
               Level = ifelse(type == "pos", "Resistance", "Species"))
    
    return(r)
}
```


#### Acinetobacter ROC & PR Curves
```{r plotAb}
abTitle <- expression(italic("A. baumannii"))

abFullRoc <- combineResults(abRoc, sfRes$sfAbRoc, type = "species") %>%
    full_join(combineResults(abRoc, sfRes$sfAbRoc, type = "pos"))
plotCurve(abFullRoc, type = "ROC", title = abTitle)
ggsave("../results/AbRocCurve.pdf", width = 70, height = 50, units = "mm", useDingbats = F)

abFullPr <- combineResults(abPr, sfRes$sfAbPr, type = "species") %>%
    full_join(combineResults(abPr, sfRes$sfAbPr, type = "pos"))
plotCurve(abFullPr, type = "PR", title = abTitle)
ggsave("../results/AbPrCurve.pdf", width = 70, height = 50, units = "mm", useDingbats = F)
```

#### Klebsiella ROC & PR Curves
```{r plotKp}
kpTitle <- expression(italic("K. pneumoniae"))

kpFullRoc <- combineResults(kpRoc, sfRes$sfKpRoc, type = "species") %>%
    full_join(combineResults(kpRoc, sfRes$sfKpRoc, type = "pos"))
plotCurve(kpFullRoc, type = "ROC", title = kpTitle)
ggsave("../results/KpRocCurve.pdf", width = 70, height = 50, units = "mm", useDingbats = F)


# Species PR
kpFullPr <- combineResults(kpPr, sfRes$sfKpPr, type = "species") %>%
    full_join(combineResults(kpPr, sfRes$sfKpPr, type = "pos"))
plotCurve(kpFullPr, type = "PR", title = kpTitle)
ggsave("../results/KpPrCurve.pdf", width = 70, height = 50, units = "mm", useDingbats = F)

```

### Plot Curve Stats
```{r curveStatsRCool}
curveStatPlot <- curveStat %>%
    full_join(sfCurveStat) %>%
    ungroup() %>%
    mutate(org = ifelse(org == "Ab", "A. baumannii", "K. pneumoniae"),
           level = ifelse(level == "Res", "Resistance", "Species"),
           classifier = str_replace(classifier, " ", "\n"))

curveStatPlot %>%
    filter(org == "A. baumannii")  %>%
    ggplot(aes(x = fct_rev(classifier), y = avg_AUC, fill = fct_rev(level),
               ymin = ci_low, ymax = ci_high)) +
    geom_col(color = "black", position = dodge) +
    geom_errorbar(position = dodge, width = 0.25) +
    facet_wrap(~fct_rev(type), nrow = 1) +
    ylab("Area Under the Curve") +
    xlab("Classifier") +
    scale_fill_discrete(name = "Level") +
    theme(legend.key.size = unit(0.5, "lines"),
          legend.margin = margin(l = -0.5, 
                                 r = -0.2)) +
    ggtitle(expression(italic("A. baumannii")))

ggsave("../results/abCurveSummary.pdf", width = 105, height = 50, units = "mm", useDingbats = F)

curveStatPlot %>%
    filter(org == "K. pneumoniae")  %>%
    ggplot(aes(x = fct_rev(classifier), y = avg_AUC, fill = fct_rev(level),
               ymin = ci_low, ymax = ci_high)) +
    geom_col(color = "black", position = dodge) +
    geom_errorbar(position = dodge, width = 0.25) +
    facet_wrap(~fct_rev(type), nrow = 1) +
    ylab("Area Under the Curve") +
    xlab("Classifier") +
    scale_fill_discrete(name = "Level") +
    theme(legend.key.size = unit(0.5, "lines"),
          legend.margin = margin(l = -0.5, 
                                 r = -0.2,
                                 unit = "lines")) +
    ggtitle(expression(italic("K. pneumoniae")))

ggsave("../results/kpCurveSummary.pdf", width = 105, height = 50, units = "mm", useDingbats = F)
```


## Select 97% Sensitivity Threshold
```{r confusionMats, results='markup'}
pickThold <- function(curve, minSens) {
    dat <- as.data.frame(curve$curve)
    dat <- dat[dat[ , 2] >= minSens, ]
    dat <- dat[dat[ , 3] == max(dat[ , 3]), ]
    names(dat) <- c("FPR", "TPR", "threshold")
    
    return(dat)
} 

# For XGBoost Classifiers
thold <- tibble(type = c("Ab_species", "Ab_resistant","Kp_species", "Kp_resistant"),
                curves = list(abRoc$species, 
                              abRoc$pos,
                              kpRoc$species, 
                              kpRoc$pos)) %>%
    group_by(type) %>%
    do(pickThold(curve = .$curves[[1]], 0.97)) %>%
    mutate(classifier = "XGBoost")

abRes2 <- abRes %>% 
    mutate(posPred = ifelse(pos >= thold$threshold[thold$type == "Ab_resistant"],
                            "pos", "neg"),
           posTruth = ifelse(truth == "pos", "pos", "neg"),
           specPred = ifelse(speciesVsOther >= thold$threshold[thold$type == "Ab_species"],
                              "Ab", "other"),
           specTruth = ifelse(truth != "other", "Ab", "other"))


kpRes2 <- kpRes %>%
    mutate(posPred = ifelse(pos >= thold$threshold[thold$type == "Kp_resistant"],
                            "pos", "neg"),
           posTruth = ifelse(truth == "pos", "pos", "neg"),
           specPred = ifelse(speciesVsOther >= thold$threshold[thold$type == "Kp_species"],
                             "Kp", "other"),
           specTruth = ifelse(truth != "other", "Kp", "other"))


# For sf Classifiers
sfthold <- tibble(type = c("Ab_species", "Ab_resistant","Kp_species", "Kp_resistant"),
                  curves = list(sfRes$sfAbRoc$species, 
                                sfRes$sfAbRoc$pos,
                                sfRes$sfKpRoc$species, 
                                sfRes$sfKpRoc$pos)) %>%
    group_by(type) %>%
    do(pickThold(curve = .$curves[[1]], 0.97)) %>%
    mutate(classifier = "Single\nFeature")


# plot for 97% Sensitivity
ratePlot <- thold %>%
    full_join(sfthold) %>%
    mutate(FNR = 1 - TPR,
           TNR = 1 - FPR) %>%
    gather(metric, value, FNR, TNR, FPR, TPR) %>%
    mutate(metricType = ifelse(metric %in% c("TPR", "FNR"), "Postives", "Negatives"),
           fills = ifelse(str_detect(metric, "T"), "good", "bad"),
           org = ifelse(str_detect(type, "Ab_"), "A. baumannii", "K. pneumoniae"),
           Level = ifelse(str_detect(type, "_resistant"), "Resistance", "Species"),
           metric = parse_factor(metric, c("TPR", "FNR", "TNR", "FPR")))


ratePlot %>%
    filter(metric == "FPR") %>%
    ggplot(aes(x = fct_rev(classifier), y = value, fill = Level)) +
    geom_col(color = "black", position = "dodge") +
    facet_wrap(~org, nrow = 1) +
    xlab("Classifier") +
    ylab("False Positive Rate (FPR)") +
    theme(legend.key.size = unit(0.5, "lines"),
          legend.margin = margin(l = -0.5, 
                                 r = -0.2,
                                 unit = "lines"),
          panel.spacing = unit(0, "lines"))
    
ggsave("../results/FPR.pdf", width = 70, height = 50, units = "mm", useDingbats = F)


ratePlot %>%
    filter(org == "A. baumannii",
           metric %in% c("TNR", "FPR")) %>%
    ggplot(aes(x = fct_rev(classifier), y = value, fill = fct_rev(metric))) + 
    geom_col(color = "black") +
    facet_wrap(~fct_rev(Level)) +
    scale_fill_discrete(name = "Metric") +
    theme(legend.key.size = unit(0.5, "lines"),
          legend.margin = margin(l = -0.5, 
                                 r = -0.2,
                                 unit = "lines"),
          axis.title.y = element_blank()) +
    ggtitle(expression(italic("A. baumannii"))) +
    xlab("Classifier")

ggsave("../results/abFPR.pdf", width = 70, height = 50, units = "mm", useDingbats = F)

ratePlot %>%
    filter(org == "K. pneumoniae",
           metric %in% c("TNR", "FPR")) %>%
    ggplot(aes(x = fct_rev(classifier), y = value, fill = fct_rev(metric))) + 
    geom_col(color = "black") +
    facet_wrap(~fct_rev(Level)) +
    scale_fill_discrete(name = "Metric") +
    theme(legend.key.size = unit(0.5, "lines"),
          legend.margin = margin(l = -0.5, 
                                 r = -0.2,
                                 unit = "lines"),
          axis.title.y = element_blank()) +
    ggtitle(expression(italic("K. pneumoniae"))) +
    xlab("Classifier")

ggsave("../results/kpFPR.pdf", width = 70, height = 50, units = "mm", useDingbats = F)

```

## Performance at 97% Sensitivity
```{r isolatePerformance}
calcIsoStats <- function(resDf, species, level) {
    
    if(level == "species") {
        cm <- confusionMatrix(data = resDf$specPred, 
                              reference = resDf$specTruth, 
                              positive = species, mode = "everything")
        
        
    } else if(level == "res") {
        cm <- confusionMatrix(data = resDf$posPred, 
                              reference = resDf$posTruth, 
                              positive = "pos", mode = "everything")
    }
    
    ret <- as.tibble(as.list(c(cm$overall, cm$byClass)))
    ret$orgResults <- species
    ret$level <- level
    
    ret <- select(ret, level, orgResults, Accuracy,
                  Sensitivity, Specificity, Precision)
    
    return(ret)
}

abSpecStats <- abRes2 %>%
    bootstrap(nboot) %>%
    do(calcIsoStats(., "Ab", "species"))

abResStats <- abRes2 %>%
    bootstrap(nboot) %>%
    do(calcIsoStats(., "Ab", "res"))

kpSpecStats <- kpRes2 %>%
    bootstrap(nboot) %>%
    do(calcIsoStats(., "Kp", "species"))

kpResStats <- kpRes2 %>%
    bootstrap(nboot) %>%
    do(calcIsoStats(., "Kp", "res"))

statOrder <- c("Accuracy", "Sensitivity", "Specificity", "Precision")

isoStats <- abSpecStats %>%
    full_join(abResStats) %>%
    full_join(kpSpecStats) %>%
    full_join(kpResStats) %>%
    gather(statistic, value, -level, -orgResults, -replicate) %>%
    group_by(level, orgResults, statistic) %>%
    summarize(avg = mean(value),
              ci_low = quantile(value, 0.05 / 2),
              ci_high = quantile(value, 1 - 0.05 / 2)) %>%
    ungroup() %>%
    mutate(statistic = fct_relevel(statistic, statOrder),
           species = str_replace(orgResults, "Ab", "A. baumannii"),
           species = str_replace(species, "Kp", "K. pneumoniae"),
           level = str_replace(level, "res", "Resistance"),
           level = str_replace(level, "species", "Species"),
           level = fct_rev(as.factor(level)))

isoStats %>%
    ggplot(aes(x = statistic, y = avg, 
               ymax = ci_high, ymin = ci_low, fill = level)) +
    geom_col(color = "black", position = dodge) +
    geom_errorbar(position = dodge, width = 0.25) +
    scale_fill_discrete(name = "Level") +
    facet_wrap(~species, ncol = 1) +
    theme(axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          legend.key.size = unit(0.5, "lines"),
          legend.margin = margin(l = -0.5, 
                                 r = -0.2,
                                 unit = "lines"))

ggsave("../results/isoStats.pdf", width = 140, height = 100, units = "mm", useDingbats = F)
```


## Variable Importance
```{r varImp}
vImpAb <- xgb.importance(colnames(testdmatList$Ab$dat), model = abMod) %>%
    mutate(org = "Ab")

vImpKp <- xgb.importance(colnames(testdmatList$Kp$dat), model = kpMod) %>%
    mutate(org = "Kp")

abFeats <- str_replace(vImpAb$Feature, "mz", "")
kpFeats <- str_replace(vImpKp$Feature, "mz", "")

basePeaks <- c(nom2feat(1910, abFeats), # Ab
               nom2feat(1894, abFeats),
               nom2feat(1882, abFeats),
               nom2feat(1840, kpFeats), # Kp
               nom2feat(1824, kpFeats),
               nom2feat(2063, kpFeats),
               nom2feat(2079, kpFeats))

resPeaks <- c(nom2feat(2033, abFeats), # Ab
              nom2feat(2005, abFeats),
              nom2feat(1955, kpFeats), # Kp
              nom2feat(1971, kpFeats))#,
              #nom2feat(1895, kpFeats))

vImp <- vImpAb %>%
    full_join(vImpKp) %>%
    mutate(featureMz = as.factor(str_replace(Feature, "mz", "")),
           featureMz = fct_reorder(featureMz, Gain, .desc = T),
           color = ifelse(featureMz %in% basePeaks, "Published Base Lipid A Structure", NA),
           color = ifelse(featureMz %in% resPeaks, 
                          "Published Resistance Lipid A Structure", color)) %>%
    group_by(org) %>%
    arrange(desc(Gain)) %>%
    filter(Gain >= Gain[20])

# Acinetobacter
vImp %>%
    filter(org == "Ab") %>%
    ggplot(aes(x = featureMz, y = Gain, ymax = Gain, ymin = 0)) +
    geom_linerange(size = 0.75) +
    geom_point(size = 2, aes(color = color)) +
    xlab(expression(paste("Feature (", italic("m/z"), ")"))) +
    scale_color_discrete(breaks = c("Base Lipid A Structure", "Resistance Lipid A Structure")) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
          legend.position = c(0.996, 0.992),
          legend.justification = c(1, 1),
          legend.title = element_blank(),
          legend.background = element_rect(color = "black"),
          legend.key.size = unit(0.5, "lines"),
          legend.margin = margin(t = 0, b = 0.2, l = 0.2, r = 0.2,  unit = "lines"),
          plot.title = element_text(margin = margin(b = 0.5, unit = "lines"))) +
    ggtitle(expression(italic("A. baumannii")))

ggsave("../results/vImpAbPlot.pdf", width = 70, height = 50, units = "mm", useDingbats = F)

saveRDS(vImpAb, "../temp/vImpAb.rds")

# Klebsiella
vImp %>%
    filter(org == "Kp") %>%
    ggplot(aes(x = featureMz, y = Gain, ymax = Gain, ymin = 0)) +
    geom_linerange(size = 0.75) +
    geom_point(size = 2, aes(color = color)) +
    xlab(expression(paste("Feature (", italic("m/z"), ")"))) +
    scale_color_discrete(breaks = c("Base Lipid A Structure", "Resistance Lipid A Structure")) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
          legend.position = c(0.996, 0.992),
          legend.justification = c(1, 1),
          legend.title = element_blank(),
          legend.background = element_rect(color = "black"),
          legend.key.size = unit(0.5, "lines"),
          legend.margin = margin(t = 0, b = 0.2, l = 0.2, r = 0.2,  unit = "lines"),
          plot.title = element_text(margin = margin(b = 0, unit = "lines"))) +
    ggtitle(expression(italic("K. pneumoniae")))

ggsave("../results/vImpKpPlot.pdf", width = 70, height = 50, units = "mm", useDingbats = F)

saveRDS(vImpKp, "../temp/vImpKp.rds")
```

## Performance on Simulated Mixture Spectra  
```{r loadMixtureData}
# Import simulated mixture spectra features and information
mixedSumm <- readRDS("../temp/complexSpectraSummary.rds")
mixedComponents <- readRDS("../temp/complexComponents.rds")

mixedList <- readRDS("../temp/mixtureDatList.rds")

mixedDmatList <- prepareData(mixedList, orgLabs = c("Ab", "Kp"))
```

### Acinetobacter baumannii  
```{r mixedAbCm}
mixedAbRes <- formatResults(abMod, mixedDmatList$Ab) %>%
    cbind(., mixedList$Ab) %>%
    select(-starts_with("mz")) %>%
    mutate(orgResults = "A. baumannii") %>%
    as_tibble(.)

mixedAbPRall <- mixedAbRes %>%
    group_by(orgResults) %>%
    do(prPos = pr.curve(.$pos[.$truth == "pos"], .$pos[.$truth != "pos"], curve = T),
       prSpecies = pr.curve(.$speciesVsOther[.$truth != "other"], 
                            .$speciesVsOther[.$truth ==  "other"], curve = T),
       rocPos = roc.curve(.$pos[.$truth == "pos"], .$pos[.$truth != "pos"], curve = T),
       rocSpecies = roc.curve(.$speciesVsOther[.$truth != "other"], 
                            .$speciesVsOther[.$truth ==  "other"], curve = T)) %>%
    mutate(prPosAUC = prPos$auc.integral,
           prSpeciesAUC = prSpecies$auc.integral,
           rocPosAUC = rocPos$auc,
           rocSpeciesAUC = rocSpecies$auc,
           n = "Overall")

mixedAbPRByn <- mixedAbRes %>%
    group_by(orgResults, n) %>%
    do(prPos = pr.curve(.$pos[.$truth == "pos"], .$pos[.$truth != "pos"], curve = T),
       prSpecies = pr.curve(.$speciesVsOther[.$truth != "other"], 
                            .$speciesVsOther[.$truth ==  "other"], curve = T),
       rocPos = roc.curve(.$pos[.$truth == "pos"], .$pos[.$truth != "pos"], curve = T),
       rocSpecies = roc.curve(.$speciesVsOther[.$truth != "other"], 
                            .$speciesVsOther[.$truth ==  "other"], curve = T)) %>%
    mutate(prPosAUC = prPos$auc.integral,
           prSpeciesAUC = prSpecies$auc.integral,
           rocPosAUC = rocPos$auc,
           rocSpeciesAUC = rocSpecies$auc)

mixedAbCurves <- mixedAbPRall %>% rbind(mixedAbPRByn)

saveRDS(mixedAbRes, file = "../temp/mixedAbRes.rds")
```

### Klebsiella pneumoniae
```{r mixedKpCm}
mixedKpRes <- formatResults(kpMod, mixedDmatList$Kp) %>%
    cbind(., mixedList$Kp) %>%
    select(-starts_with("mz"))%>%
    mutate(orgResults = "K. pneumoniae") %>%
    as_tibble(.)

mixedKpAll <- mixedKpRes %>%
    group_by(orgResults) %>%
    do(prPos = pr.curve(.$pos[.$truth == "pos"], .$pos[.$truth != "pos"], curve = T),
       prSpecies = pr.curve(.$speciesVsOther[.$truth != "other"], 
                            .$speciesVsOther[.$truth ==  "other"], curve = T),
       rocPos = roc.curve(.$pos[.$truth == "pos"], .$pos[.$truth != "pos"], curve = T),
       rocSpecies = roc.curve(.$speciesVsOther[.$truth != "other"], 
                            .$speciesVsOther[.$truth ==  "other"], curve = T)) %>%
    mutate(prPosAUC = prPos$auc.integral,
           prSpeciesAUC = prSpecies$auc.integral,
           rocPosAUC = rocPos$auc,
           rocSpeciesAUC = rocSpecies$auc,
           n = "Overall")

mixedKpByn <- mixedKpRes %>%
    group_by(orgResults, n) %>%
    do(prPos = pr.curve(.$pos[.$truth == "pos"], .$pos[.$truth != "pos"], curve = T),
       prSpecies = pr.curve(.$speciesVsOther[.$truth != "other"], 
                            .$speciesVsOther[.$truth ==  "other"], curve = T),
       rocPos = roc.curve(.$pos[.$truth == "pos"], .$pos[.$truth != "pos"], curve = T),
       rocSpecies = roc.curve(.$speciesVsOther[.$truth != "other"], 
                            .$speciesVsOther[.$truth ==  "other"], curve = T)) %>%
    mutate(prPosAUC = prPos$auc.integral,
           prSpeciesAUC = prSpecies$auc.integral,
           rocPosAUC = rocPos$auc,
           rocSpeciesAUC = rocSpecies$auc)

mixedKpCurves <- mixedKpAll %>% rbind(mixedKpByn)

# All PR and ROC results
mixedCurves <- mixedKpCurves %>% rbind(mixedAbCurves)

saveRDS(mixedKpRes, file = "../temp/mixedKpRes.rds")
```

### Plot PR and ROC curves for Simulated Mixtures by Number of Spectra in Mixture
```{r simMixPlot}
mixedCurveDat <- mixedCurves %>%
    select(-ends_with("AUC")) %>%
    gather(curveType, curveDat, -n, -orgResults) %>%
    group_by(orgResults, n, curveType) %>% 
    do(curveDf = as_tibble(.$curveDat[[1]]$curve)) %>%
    ungroup() %>%
    unnest(curveDf) %>%
    rename("Rec_Spec" = V1, "Prec_Sens" = V2, "Threshold" = V3) %>%
    mutate(PrOrRoc = ifelse(str_detect(curveType, "pr"), "PR", "ROC"),
           type = ifelse(str_detect(curveType, "Pos"), "Resistance", "Species"), #type),
           type = as.factor(type))

mixedCurveDat %>%
    filter(PrOrRoc == "PR") %>%
    ggplot(aes(x = Rec_Spec, y = Prec_Sens, color = n)) +
    geom_path() +
    coord_equal() +
    facet_grid(orgResults ~ type) +
    xlab("Recall") +
    ylab("Precision") +
    ylim(0, 1) +
    xlim(0, 1) +
    scale_color_discrete(name = "Number of Species") +
    theme(legend.key.size = unit(0.75, "lines"),
          legend.margin = margin(t = -0.5, unit = "lines"),
          legend.position = "bottom",
          axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1))

ggsave("../results/mixturePRCurves.pdf", width = 70, height = 80, units = "mm", useDingbats = F)


mixedCurveDat %>%
    filter(PrOrRoc == "ROC") %>%
    ggplot(aes(x = Rec_Spec, y = Prec_Sens, color = n)) +
    geom_abline(xintercept = 0, slope = 1) +
    geom_path() +
    coord_equal() +
    facet_grid(orgResults ~ type) +
    xlab("1 - Specificity (FPR)") +
    ylab("Sensitivity (TPR)") +
    ylim(0, 1) +
    xlim(0, 1) +
    scale_color_discrete(name = "Number of Species") +
    theme(legend.key.size = unit(0.75, "lines"),
          legend.margin = margin(t = -0.5, unit = "lines"),
          legend.position = "bottom",
          axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1))

ggsave("../results/mixtureROCCurves.pdf", width = 70, height = 80, units = "mm", useDingbats = F)
```


### Plot the AUC of PR and ROC Curves With Increasing Matrix Complexity  
```{r simAuc}
mixedCurveStats <- mixedKpRes %>%
    full_join(mixedAbRes) %>%
    nest(-n, -orgResults) %>%
    mutate(AUC = map(data, ~ bootstrap(., nboot) %>% do(calcAUC(.)))) %>%
    unnest(AUC) %>%
    group_by(n, orgResults, type, level) %>%
    summarize(avg_AUC = mean(AUC),
              ci_low = quantile(AUC, 0.05 / 2),
              ci_high = quantile(AUC, 1 - 0.05 / 2)) %>%
    mutate(level = str_replace(level, "Res", "Resistance"))
    


labOrder <- c("Species", 
              "Resistance")

mixedCurveStats %>%
    ggplot(aes(x = as.numeric(n), y = avg_AUC, color = fct_rev(level))) +
    geom_line() +
    geom_point() + 
    geom_errorbar(aes(ymax = ci_high, ymin = ci_low), width = 0.25) +
    xlab("Number of Species in Mixture") +
    ylab("Area Under the Curve") +
    ylim(c(0, 1)) +
    coord_fixed(ratio = 4) +
    scale_color_discrete(name = "Level") +
    facet_grid(fct_rev(type) ~ orgResults) +
    theme(legend.key.size = unit(0.75, "lines"),
          legend.margin = margin(t = -0.5, unit = "lines"),
          legend.position = "bottom")

ggsave("../results/mixedCurvesAUCPlot.pdf", width = 70, height = 80, units = "mm", useDingbats = F)
```

```{r otherSimStats, results = 'markup'}
mixedThold <- mixedCurveDat %>%
    filter(PrOrRoc == "ROC",
           n == "Overall") %>%
    group_by(orgResults, type) %>%
    summarise(threshold = max(Threshold[Prec_Sens >= 0.97])) %>%
    mutate(type2 = tolower(str_replace(type, "Colistin-", "")),
           species = str_replace(orgResults, "\\. ", ""),
           species = str_match(species, "^.."),
           type = paste0(species, "_", type2)) %>%
    select(-species, -type2)

mixedThold # 97% Sensitivity Thresholds for Simulated Mixtures

mixedAbRes <- mixedAbRes %>%
    mutate(posPred = ifelse(pos >= mixedThold$threshold[mixedThold$type == "Ab_resistance"],
                            "pos", "neg"),
           posTruth = ifelse(truth == "pos", "pos", "neg"),
           specPred = ifelse(speciesVsOther >= mixedThold$threshold[mixedThold$type == "Ab_species"],
                             "Ab", "other"),
           specTruth = ifelse(truth != "other", "Ab", "other"))


mixedKpRes <- mixedKpRes %>%
    mutate(posPred = ifelse(pos >= mixedThold$threshold[mixedThold$type == "Kp_resistance"],
                            "pos", "neg"),
           posTruth = ifelse(truth == "pos", "pos", "neg"),
           specPred = ifelse(speciesVsOther >= mixedThold$threshold[mixedThold$type == "Kp_species"],
                             "Kp", "other"),
           specTruth = ifelse(truth != "other", "Kp", "other"))

# Function to calculate Species Stats
specStats <- function(resDf, posClass) {
    d1 <- map_df(1:5, function(n) {
        cm <- confusionMatrix(data = resDf$specPred[resDf$n == n], 
                              reference = resDf$specTruth[resDf$n == n], 
                              positive = posClass, mode = "everything")
        
        data.frame(as.list(c(cm$overall, cm$byClass)))
    })
    
    cm2 <- confusionMatrix(data = resDf$specPred, 
                           reference = resDf$specTruth, 
                           positive = posClass, mode = "everything")
    
    ret <- rbind(data.frame(as.list(c(cm2$overall, cm2$byClass))), d1)
    ret$n <- c("Overall", 1, 2, 3, 4, 5)
    ret$orgResults <- resDf$orgResults[1]
    
    ret <- select(ret, orgResults, n, Accuracy,
                  Sensitivity, Specificity, Precision)

    
    return(ret)
}

# Species Stats
mixedAbSpecStats <- mixedAbRes %>%
    bootstrap(nboot) %>%
    do(specStats(., "Ab"))

mixedKpSpecStats <- mixedKpRes %>%
    bootstrap(nboot) %>%
    do(specStats(., "Kp"))

mixedSpecStats <- mixedAbSpecStats %>%
    full_join(mixedKpSpecStats) %>%
    gather(statistic, value, -orgResults, -n, -replicate) %>%
    group_by(orgResults, n, statistic) %>%
    summarize(avg = mean(value),
              ci_low = quantile(value, 0.05 / 2),
              ci_high = quantile(value, 1 - 0.05 / 2))





# Function to calculate Resistance Stats
resStats <- function(resDf, posClass = "pos") {
    d1 <- map_df(1:5, function(n) {
        cm <- confusionMatrix(data = resDf$posPred[resDf$n == n], 
                              reference = resDf$posTruth[resDf$n == n], 
                              positive = posClass, mode = "everything")
        
        data.frame(as.list(c(cm$overall, cm$byClass)))
    })
    
    cm2 <- confusionMatrix(data = resDf$posPred, 
                           reference = resDf$posTruth, 
                           positive = posClass, mode = "everything")
    
    ret <- rbind(data.frame(as.list(c(cm2$overall, cm2$byClass))), d1)
    ret$n <- c("Overall", 1, 2, 3, 4, 5)
    ret$orgResults <- resDf$orgResults[1]
    
    ret <- select(ret, orgResults, n, Accuracy,
                  Sensitivity, Specificity, Precision)
    
    return(ret)
}

# Resistance Stats
mixedAbResStats <- mixedAbRes %>%
    bootstrap(nboot) %>%
    do(resStats(.))

mixedKpResStats <- mixedKpRes %>%
    bootstrap(nboot) %>%
    do(resStats(.))

mixedResStats <- mixedAbResStats %>%
    full_join(mixedKpResStats) %>%
    gather(statistic, value, -orgResults, -n, -replicate) %>%
    group_by(orgResults, n, statistic) %>%
    summarize(avg = mean(value),
              ci_low = quantile(value, 0.05 / 2),
              ci_high = quantile(value, 1 - 0.05 / 2))

```

### Plot statistics from simulated mixtures
```{r mixedStatisticsPlots}
mixedSpecStats %>%
    ggplot(aes(x = n, y = avg, ymax = ci_high, ymin = ci_low)) +
    geom_col(position = "dodge", color = "black") +
    geom_errorbar(width = 0.25) +
    facet_grid(orgResults ~ statistic) +
    ylab("Value") +
    xlab("Number of Species in Mixture") +
    ggtitle("Species-Level Detection")

ggsave("../results/simSpecStats.pdf", width = 210, height = 80, units = "mm", useDingbats = F)

mixedResStats %>%
    ggplot(aes(x = n, y = avg, ymax = ci_high, ymin = ci_low)) +
    geom_col(position = "dodge", color = "black") +
    geom_errorbar(width = 0.25) +
    facet_grid(orgResults ~ statistic) +
    ylab("Value") +
    xlab("Number of Species in Mixture") +
    ggtitle("Colistin Resistance Detection")

ggsave("../results/simResStats.pdf", width = 210, height = 80, units = "mm", useDingbats = F)
```



## Two-Species UTI Mixtures
```{r twoSpecies}
# Import simulated mixture spectra features and information
twoSpeciesSumm <- readRDS("../temp/twoSpeciesSpecInfo.rds")

twoSpeciesList <- readRDS("../temp/twoSpeciesDatList.rds")

twoSpeciesDmatList <- prepareData(twoSpeciesList, orgLabs = c("Ab", "Kp"))

# predict 
twoAbRes <- formatResults(abMod, twoSpeciesDmatList$Ab) %>%
    cbind(., twoSpeciesList$Ab) %>%
    select(-starts_with("mz"))%>%
    mutate(orgResults = "A. baumannii",
           percentTarget = ifelse(truth == "other", 0, 100 - percentEc),
           Colistin = ifelse(percentTarget > 0 & truth != "other", as.character(truth), NA),
           Colistin = str_replace(Colistin, "pos", "resistant"),
           Colistin = str_replace(Colistin, "neg", "susceptible")) %>%
    as_tibble(.)

twoKpRes <- formatResults(kpMod, twoSpeciesDmatList$Kp) %>%
    cbind(., twoSpeciesList$Kp) %>%
    select(-starts_with("mz"))%>%
    mutate(orgResults = "K. pneumoniae",
           percentTarget = ifelse(truth == "other", 0, 100 - percentEc),
           Colistin = ifelse(percentTarget > 0 & truth != "other", as.character(truth), NA),
           Colistin = str_replace(Colistin, "pos", "resistant"),
           Colistin = str_replace(Colistin, "neg", "susceptible")) %>%
    as_tibble(.)


twoRes <- twoAbRes %>% 
    full_join(twoKpRes) %>%
    mutate(Colistin = fct_rev(as.factor(Colistin))) %>%
    filter(!(truth == "other" & percentEc != 100)) %>%
    group_by(Colistin, percentTarget, orgResults) %>%
    mutate(avg_speciesVsOther = mean(log10(speciesVsOther)),
           avg_pos = mean(log10(pos)),
           ci_lo_speciesVsOther = t.test(log10(speciesVsOther))$conf.int[1],
           ci_hi_speciesVsOther = t.test(log10(speciesVsOther))$conf.int[2],
           ci_lo_pos = t.test(log10(pos))$conf.int[1],
           ci_hi_pos = t.test(log10(pos))$conf.int[2])

twoResSumm <- twoRes %>%
    group_by(Colistin, percentTarget, orgResults) %>%
    summarize(avg_speciesVsOther = mean(log10(speciesVsOther)),
              avg_pos = mean(log10(pos)),
              ci_lo_speciesVsOther = t.test(log10(speciesVsOther))$conf.int[1],
              ci_hi_speciesVsOther = t.test(log10(speciesVsOther))$conf.int[2],
              ci_lo_pos = t.test(log10(pos))$conf.int[1],
              ci_hi_pos = t.test(log10(pos))$conf.int[2])

saveRDS(twoAbRes, file = "../temp/twoAbRes.rds")
saveRDS(twoKpRes, file = "../temp/twoKpRes.rds")
```

### Plot scores vs cutoff
```{r twoSpecScores}
tholdSpecies <- mixedThold %>%
    filter(str_detect(type, "species"))

twoRes %>%
    ggplot(aes(x = as.factor(percentTarget), y = log10(speciesVsOther),
               fill = Colistin, group = Colistin)) +
    geom_errorbar(aes(ymax = ci_hi_speciesVsOther, 
                      ymin = ci_lo_speciesVsOther, 
                      color = Colistin), 
                  width = 0.25, position = dodge) +
    geom_crossbar(aes(ymax = avg_speciesVsOther, ymin = avg_speciesVsOther, 
                      y = avg_speciesVsOther, color = Colistin),
                  width = 0.5, fatten = 1, 
                  position = dodge, show.legend = F) +
    geom_point(width = 0.25, shape = 21, position = position_jitterdodge()) +
    facet_wrap(~orgResults, ncol = 2) +
    scale_fill_discrete(breaks = c("resistant", "susceptible")) +
    scale_color_discrete(guide = "none") +
    xlab("Percent Target Species by Volume") +
    ylab("Colistin Resistance log(Score)") +
    theme(legend.key.size = unit(0.75, "lines"),
          legend.margin = margin(t = -0.5, unit = "lines"),
          legend.position = "bottom")

ggsave("../results/twoSpeciesSpecRes.pdf", width = 105, height = 60, units = "mm", useDingbats = F)


tholdRes <- mixedThold %>%
    filter(str_detect(type, "res"))

twoRes %>%
    ggplot(aes(x = as.factor(percentTarget), y = log10(pos), 
               fill = Colistin, group = Colistin)) +
    geom_errorbar(aes(ymax = ci_hi_pos, ymin = ci_lo_pos, color = Colistin), 
                  width = 0.25, position = dodge) +
    geom_crossbar(aes(ymax = avg_pos, ymin = avg_pos, 
                      y = avg_pos, color = Colistin),
                  width = 0.5, fatten = 1, 
                  position = dodge, show.legend = F) +
    geom_point(width = 0.25, shape = 21, position = position_jitterdodge()) +
    facet_wrap(~orgResults, ncol = 2) +
    scale_fill_discrete(breaks = c("resistant", "susceptible")) +
    scale_color_discrete(guide = "none") +
    xlab("Percent Target Species by Volume") +
    ylab("Colistin Resistance log(Score)") +
    theme(legend.key.size = unit(0.75, "lines"),
          legend.margin = margin(t = -0.5, unit = "lines"),
          legend.position = "bottom")
    #ylim(c(0, 1))

ggsave("../results/twoSpeciesResRes.pdf", width = 105, height = 60, units = "mm", useDingbats = F)
    

```

## Session Info  
```{r sessionInfo, results='markup'}
session_info()
```

