---
title: "Simulating Glycolipid MALDI-TOF-MS of Complex Samples"
Author: "William E Fondrie"
output: github_document
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE, 
                      results = "hide", 
                      cache = T)
```

# Introduction 
This file contains the code to simulate glycolipid MALDI-TOF mass spectra of organism mixtures using linear combinations of the real glycolipid mass spectra in our library. **Warning**: Running this code requires a minimum of ~50 Gb of RAM to execute. The machine this was run on had 64 Gb of RAM and 2x AMD Opteron 6272 processors (2.10 GHz).  

# Load Libraries & Prepare Workspace
```{r loadLibraries}
suppressMessages(library(tidyverse, quietly = T))
library(MALDIquant, quietly = T)
library(MALDIquantForeign, quietly = T)
library(stringr, quietly = T)
library(forcats, quietly = T)
library(tictoc, quietly = T)
library(devtools, quietly = T)

source("../R/preProcessSpec.R")
source("../R/extract.R")
source("../R/ggplotTheme.R")
source("../R/createNewFeatureTbl.R")

set.seed(6578548)
tic()

featTol <- readRDS("../temp/mzTol.rds") # load feature extraction tolerance
```

# Retrieve File Information  
```{r importSpectra}
files <- list.files("../data/fullLib", 
                    full.names = T, 
                    pattern = "mzXML$",
                    recursive = T)
#files <- sample(files, 50)

specInfo <- tibble(fname = files) %>%
    mutate(type = str_match(fname, "([^\\^/]+)[\\/][^\\^/]+mzXML$")[ , 2],
           id = str_match(fname, "([^\\^/]+).mzXML$")[ , 2],
           species = str_match(type, "^[^ ]+ [^ ]+")[ , 1],
           Ab = ifelse(str_detect(type, "Acinetobacter baumannii - res"), "pos", "other"),
           Kp = ifelse(str_detect(type, "Klebsiella pneumoniae - res"), "pos", "other"),
           Ab = as.factor(ifelse(str_detect(type, "Acinetobacter baumannii - sen"), "neg", Ab)),
           Kp = as.factor(ifelse(str_detect(type, "Klebsiella pneumoniae - sen"), "neg", Kp)))

summary(specInfo)

```

# Select Linear Combinations  
```{r combinations, results = "hold"}
selectLinearCombos <- function(n, info) {
    
    regex <- "(Acinetobacter baumannii|Klebsiella pneumoniae)"
    pAbKp <- 0.3/n
    res <- sample(c(" - res", " - sen"), 1) # 50:50 shot of res or sen
    
    speciesSelect <- info %>%
        group_by(species) %>%
        summarize(num = length(id)) %>%
        mutate(weights = ifelse(str_detect(species, regex), 
                                pAbKp, 
                                (1-2*pAbKp)/(length(species)-2))) %>%
        sample_n(size = n, weight = weights)
    
    selected <- speciesSelect %>%
        left_join(info) %>%
        filter(type != paste0(species, res)) %>%
        group_by(species) %>%
        sample_n(size = 1) %>%
        ungroup() %>%
        sample_frac(size = 1) %>%
        mutate(coeff = c(1, sample(c(1, 0.5, 0.25, 0.1), n-1, replace = T)))
    
    return(selected)
}

numSpecies <- rep(c(1:5), 1000) # number of spectra to simulate
#numSpecies <- rep(c(1:5), 1) # test line

combos <- tibble(spec_id = as.factor(paste0("spec_", 1:length(numSpecies))),
                 comp = map(numSpecies, selectLinearCombos, info = specInfo)) %>%
    unnest()

fctOrder <- c("neg", "other", "pos")

comboSummary <- combos %>%
    group_by(spec_id) %>%
    summarize(n = length(id),
              AbCoeff = ifelse(any(Ab != "other"), coeff[Ab != "other"] / max(coeff), 0),
              KpCoeff = ifelse(any(Kp != "other"), coeff[Kp != "other"] / max(coeff), 0),
              AbPres = ifelse(any(Ab == "pos"), "pos", "other"),
              KpPres = ifelse(any(Kp == "pos"), "pos", "other"),
              AbPres = as.factor(ifelse(any(Ab == "neg"), "neg", AbPres)),
              KpPres = as.factor(ifelse(any(Kp == "neg"), "neg", KpPres))) %>%
    rename(Ab = AbPres, Kp = KpPres) %>%
    mutate(Ab = fct_relevel(Ab, fctOrder),
           Kp = fct_relevel(Kp, fctOrder))

saveRDS(comboSummary, file = "../temp/complexSpectraSummary.rds")
saveRDS(combos, file = "../temp/complexComponents.rds")

summary(comboSummary)

comboSummary %>%
    group_by(n) %>%
    summarize(numAb = sum(Ab != "other"),
              numKp = sum(Kp != "other"),
              numOther = sum(Ab == "other" & Kp == "other"),
              numPosAb = sum(Ab == "pos"),
              numPosKp = sum(Kp == "neg"))
```

# Create Complex Spectra from Selections And Extract Features  
```{r createSpectra}
# list of features, created in rmd/modelTraining.rmd
features <- readRDS("../temp/features.rds")

specList <- preProcessSpec(files, hws = 80) # Same preprocessing

# rm files that contain multiple spectra
multiSpecIdx <- map_lgl(specList, ~ metaData(.)$num > 1)
specList <- specList[!multiSpecIdx]

spec <- map_df(specList, extractSpectra)

gc() # garbage collection. Free as much memory as possible.

# Takes ~30 min
comboSpec <- combos %>% 
    left_join(spec) %>%
    group_by(spec_id) %>%
    group_by(spec_id, id, type) %>%
    do(massSpecObj = createMassSpectrum(mass = .$mz, intensity = .$relInt, 
                                        metaData = list(file = paste0("/cmb/", .$spec_id[1], ".mzXML")))) %>%
    group_by(spec_id) %>%
    do(massSpecObj = averageMassSpectra(.$massSpecObj, method = "sum")) %>%
    do(extractSpectra(.$massSpecObj))

saveRDS(comboSpec, "../temp/comboSpec.rds")

trainIdx <- readRDS("../temp/trainIdx.rds")


createMixtureFeatureTbl <- function(trainList, specDf, summaryDat, mzTol) {
    suffix <- if(str_detect(trainList$regex, "Acineto")) "_Ab" else "_Kp"
    
    # extract specified features
    cat(paste0("Creating features for ", suffix, "...\n"))
    feattbl <- specDf %>%
      group_by(id) %>%
      do(extractFeatures(., featureVec = trainList$features, tol = mzTol))
    
    saveRDS(feattbl, file = paste0("../temp/mixtureFeatureInfo", suffix, ".rds"))
    
    mlFeat <- feattbl %>%
        select(id, feat, relInt) %>%
        group_by(id) %>%
        mutate(relInt = relInt / max(relInt)) %>%
        ungroup() %>%
        spread(key = feat, value = relInt, fill = 0) %>%
        left_join(summaryDat, by = c("id" = "spec_id")) 
    
    return(mlFeat)
}

# extract features for prediction
mixtureDatList <- map(trainIdx,createMixtureFeatureTbl, 
                      specDf = comboSpec,
                      summaryDat = comboSummary,
                      mzTol = featTol)

saveRDS(mixtureDatList, file = "../temp/mixtureDatList.rds")
```

# Session Information  
```{r SessionInfo, results = "hold"}
times <- toc()

cat(c("Execution time:", round((times$toc - times$tic)/60, 0), "min\n\n"))

session_info()
```



