---
title: "Machine learning enables pathogen identification and detection of antimicrobial resistance from mass spectrometry analysis of membrane glycolipids"
author: "William E Fondrie, "  
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
    github_document:
        html_preview: false
        toc: true
        toc_depth: 3
---

```{r, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE,
                      results = "hide",
                      fig.show = "hide")

knitr::opts_knit$set(verbose = TRUE)
```


## Introduction
This repository contains the code and data required to reproduce the analysis presented in [*Machine learning enables pathogen identification and detection of antimicrobial resistance from mass spectrometry analysis of membrane glycolipids*]().  

**WARNING:** When attempting to reproduce this analysis, it should be noted that `Rmd/simulateCompleSpectra.Rmd` requires approximately 36 Gb of memory to execute. Additionally, the entire analysis time may take a number of hours depending on the hardware.

Order of analysis (see the Rmd subdirectory for details): 
1. [modelTraining.Rmd](Rmd/mdOutput/modelTraining.md)  
2. [simulateComplexSpectra.Rmd](Rmd/mdOutput/simulateComplexSpectra.md)  
3. [mixtureAnalysis.Rmd](Rmd/mdOutput/mixtureAnalysis.md)  
4. [evaluateModels.Rmd](Rmd/mdOutput/evaluateModels.md)  
5. [baselineClassifiers.Rmd](Rmd/mdOutput/baselineClassifiers.md)  
6. [makeMiscFigures.Rmd](Rmd/mdOutput/makeMiscFigures.md)  
7. [illustrations.Rmd](Rmd/mdOutput/illustrations.md)  
8. [makeTables.Rmd](Rmd/mdOutput/makeTables.md)

## Directory structure  
To reproduce this analysis, the project directory must be structured as 
follows:  
```{}
|- README.Rmd
|- data
|  `- data.zip
|- R
|  |- createNewFeatureTbl.R
|  |- ggplotTheme.R
|  |- utilityFunctions.R
|  |- prepareData.R
|  |- extract.R
|  `- preProcessSpec.R
`- Rmd
   |- baselineClassifiers.Rmd
   |- evaluateModels.Rmd
   |- illustrations.Rmd
   |- makeMiscFigures.Rmd
   |- mixtureAnalysis.Rmd
   |- modelTraining.Rmd
   |- simulateComplexSpectra.Rmd
   `- writeTables.Rmd

```

## Install necessary packages  
This analysis uses a number of R packages. To ensure that all of them are installed on your machine, you can execute the following:  
```{r installPkgs, eval = FALSE}
install.packages(c("tidyverse",
                   "stringr",
                   "forcats",
                   "MALDIquant",
                   "MALDIquantForeign",
                   "caret",
                   "PRROC",
                   "xgboost",
                   "tictoc",
                   "devtools",
                   "openxlsx",
                   "e1071",
                   "knitr",
                   "rmarkdown"))
```

## Code to run the analysis 
With a correctly prepared directory, the entire analysis can be run with a single line of code. If it is your fist time running the analysis, you can unzip the `data/data.zip` into the `data` directory manually, or change `unzipData` to `TRUE` in the next section.

To run the analysis:
```{r runFullAnalysis, eval = FALSE}
rmarkdown::render("path/to/README.Rmd", envir = new.env())
```

When this rmarkdown file is rendered, the following code is executed:

### Prepare workspace
```{r prepAnalysis, eval = TRUE, results = 'hide'}
tictoc::tic()
unzipData <- FALSE # change to "TRUE" to unzip "data.zip" in the data directory

if(unzipData) {
    unzip("data/data.zip", overwrite = T, exdir = "../data")
}

library(rmarkdown)

# Make results, temp and mdOutput directories:
dir.create("temp")
dir.create("results")
dir.create("Rmd/mdOutput")

# Set global parameters for analysis
mzTol <- 1.5 # m/z tolerance for feature extraction in Da
saveRDS(mzTol, "temp/mzTol.rds")
```

### Run Analysis Scripts
The `runAnalysis()` function takes a list of `.Rmd` files and knits them into GitHub compatible markdown files. 
```{r runAnalysisFun, eval = TRUE, results = 'hide'}
runAnalysis <- function(rmd) {
    lapply(rmd, 
           render,
           envir = new.env(),
           output_dir = "Rmd/mdOutput")
}

files <- c("modelTraining", # Trains xgboost models
           "simulateComplexSpectra", # simulates polymicrobial spectra
           "mixtureAnalysis", # Imports spectra from experimental two-species
           "baselineClassifiers", # Implements simple baseline classifiers
           "evaluateModels", # Calculate performance metrics and makes figures
           "makeMiscFigures", # Creates additional figures
           "illustrations", # Creates additional figures for illustrations
           "writeTables") # Creates supplementarly Tables

files <- paste0("Rmd/", files, ".Rmd")
```

Now run the analysis:  
```{r runAnalysis, eval = TRUE, results = 'hide'}
runAnalysis(files)
```

## Session Info
```{r SessionInfo1, results = "hold", eval = TRUE}
times <- tictoc::toc()
cat(c("Execution time:", round((times$toc - times$tic)/60, 0), "min\n\n"))
session_info()
```




