---
title: "Machine learning enables pathogen identification and detection of antimicrobial resistance from mass spectrometry analysis of membrane glycolipids"
author: "William E Fondrie, "  
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
    github_document:
        html_preview: false
        toc: true
        toc_depth: 3
---

```{r, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE,
                      results = 'hide')

knitr::opts_knit$set(verbose = TRUE)
```


## Introduction
This repository contains the code and data required to reproduce the analysis presented in [*Machine learning enables pathogen identification and detection of antimicrobial resistance from mass spectrometry analysis of membrane glycolipids*]().  

**WARNING:** When attempting to reproduce this analysis, it should be noted that `Rmd/simulateCompleSpectra.Rmd` requires approximately 50 Gb of memory to execute. Additionally, the entire analysis time may take a number of hours depending on the hardware.

Order of analysis (see the Rmd subdirectory for details):  
1. [modelTraining.Rmd]("Rmd/modelTraining.md")  
2. [simulateComplexSpectra.Rmd]("Rmd/simulateComplexSpectra.md")  
3. [mixtureAnalysis.Rmd]("Rmd/mixtureAnalysis.md")  
4. [evaluateModels.Rmd]("Rmd/evaluateModels.md")    
5. [makeMiscFigures.Rmd]("Rmd/makeMiscFigures.md")  
6. [illustrations.Rmd]("Rmd/illustrations.md")  
7. [makeTables.Rmd]("Rmd/makeTables.md")

## Directory structure  
To reproduce this analysis, the project directory must be structured as 
follows:
```{}
|- README.Rmd
|- data
|  `- data.zip
|- R
|  |- createNewFeatureTbl.R
|  |- ggplotTheme.R
|  |- utilityFunctions.R
|  |- prepareData.R
|  |- extract.R
|  `- preProcessSpec.R
`- Rmd
   |- evaluateModels.Rmd
   |- illustrations.Rmd
   |- makeMiscFigures.Rmd
   |- mixtureAnalysis.Rmd
   |- modelTraining.Rmd
   |- simulateComplexSpectra.Rmd
   `- writeTables.Rmd

```

## Code to run the analysis 
With a correctly prepared directory, the entire analysis can be run with a single line of code. Also, take note of the `instPckgs` variable in the "Prepare workspace" section below. If you system does not have all of these packages already installed, change this variable to `TRUE`.

To run the analysis:
```{r runFullAnalysis, eval = FALSE}
render("path/to/README.Rmd", envir = new.env())
```

When this rmarkdown file is rendered, the following code is executed:

### Prepare workspace
```{r prepAnalysis, eval = TRUE}
instPckgs <- FALSE # change to "TRUE" to install all packages used in the analyses
unzipData <- FALSE # change to "TRUE" to unzip "data.zip" in the data directory

if(instPckgs) {
    install.packages(c("tidyverse",
                       "stringr",
                       "forcats",
                       "MALDIquant",
                       "MALDIquantForeign",
                       "caret",
                       "PRROC",
                       "xgboost",
                       "tictoc",
                       "devtools",
                       "openxlsx",
                       "knitr",
                       "rmarkdown"))
}

if(unzipData) {
    unzip("data/data.zip", overwrite = T, exdir = "../data")
}

library(rmarkdown)
library(tictoc)

tic()

# Make results and temp directories:
dir.create("temp")
dir.create("results")

# Set global parameters for analysis
mzTol <- 1.5 # m/z tolerance for feature extraction in Da
saveRDS(mzTol, "temp/mzTol.rds")
```

### Run Analysis Scripts  
```{r runAnalysis, eval = TRUE}
render("Rmd/modelTraining.Rmd", envir = new.env()) # Trains xgboost models
render("Rmd/simulateComplexSpectra.Rmd", envir = new.env()) # simulates polymicrobial spectra
render("Rmd/mixtureAnalysis.Rmd", envir = new.env()) # Imports spectra from experimental two-species mixtures
render("Rmd/evaluateModels.Rmd", envir = new.env()) # Calculate performance metrics and makes figures
render("Rmd/makeMiscFigures.Rmd", envir = new.env()) # Creates additional figures
render("Rmd/illustrations.Rmd", envir = new.env()) # Creates additional figures for illustrations
render("Rmd/writeTables.Rmd", envir = new.env()) # Creates supplementarly Tables
```


## Session Info
```{r SessionInfo1, results = "hold", eval = TRUE}
times <- toc()

cat(c("Execution time:", round((times$toc - times$tic)/60, 0), "min\n\n"))

session_info()
```




